\WorkEntry{ATH-WORK-0007}{Pivot}{%
\begin{OldSchoolEssay}
\enlargethispage{1\baselineskip}
I drove through the night. It was two thousand and three. What a cock! I had never mapped our course. Around the block I drove, and again. And again. Oh! That's where I bought Nursey. Where the fuck is the hospital? The baby is already on its way. And here I am driving belly-burst-mother around the Sunday market. All closed, of course. It was not Sunday, and even if it were, it was too late to be open. Stay focussed my witchy friend that I had left behind. I've got this.

Why the fuck hadn't I practised ahead of time? I found it. I found the hospital! I found the maternity ward. I cannot believe that I twice drove past the spot where I had bought Nursey. What the hell use was she now, anyway? \textit{Leave her alone, she goes where I go.}

Wendy's cervix was nine centimetres dilated. We could almost see your head.

There was no time left. It had been about an hour and a half since your mother dropped your amniotic fluid on our bedroom floor Ten centimetres dilation now as Wendy is lying on the birth bed. It's too late for pain relief, your mother will birth you as she is. Not even an aspirin to help.

"Push! Push! Push!'' the hospital staff urge. Your mother and father are holding hands. Damn! She was strong---nearly crushed my hand. A four inch poo came out of her bum, and a young nurse whipped it away. She looked at me hoping I did not see. More pushing. More pain. Your mother was the strongest person I had seen at that point. She pushed on. No pain relief remember. I saw your head start to show. You had wispy hair and you were covered in white shit that looked like smegma

Wendy pushed and pushed. I saw your wrinkled scrawny eyes, then your shoulders. Your mother exclaimed that nobody had told her it would burn. In fact, birthing you had torn her perineum from arse to vagina
\enlargethispage{1\baselineskip}
You plopped out. Still covered in white greasy smegma looking goo.

They put you on your mother's chest so she could hold you. Wendy said in wonder ``Oh! A baby!''

Welcome to the world Athena, ten minutes after 11pm at Falkirk Royal Infirmary, 2003.

Your placenta was firmly lodged. A doctor and midwife managed to snap your umbilical cord trying to pull everything out of Wendy's womb. One of them dipped out of the room, and came back a minute later with the daintiest female doctor you will ever see. A slim and slight Indian girl with slim limbs and tiny hands. She put her right arm all the way up the birth canal---all the way up to her elbow trying to pull your placenta out of Wendy's womb. (Seriously dude! All the way up to the elbow.)

Your placenta refused to come out, so they took your mother to surgery for a ``D\&C'', whatever that was. You had that white smegma washed off at this point. I held you so close to me. The most precious thing. Very precious. I hope you feel one day what your mother and I felt that day you were born.

They made me put you on a trolley---like one of those cake and tea trolleys, but more sturdy. I didn't want to let go of you. Our Athena. You were Athena long before your greasy white body was squeezed out of a hole that had no business being that large that day.

Your mom had your stubborn placenta surgically removed.

We slept the night with you at the hospital. Wendy in bed, you beside her in a crib, and me beside the bed in an upright armchair. I later learned that the chair was a recliner---I didn't have to be so uncomfortable all the night, which I was.

\pagebreak
Your mother became an adult that day. It was wonderful to see the change in her. It didn't last.

And now you are 21. I love you baby.

\textit{``It's coming! It's coming!''. Ohh look, that's where I bought Nursey. ``Fuck off! It's coming, it's coming. Where is the hospital!?''. I think it's over there. Oh look, we're back where I bought Nursey. ``Fuck off! It's coming, it's coming!''}

Precious times.
\end{OldSchoolEssay}
}{\VLabel{Lens:}  Reality is not polite.}{\VLabel{Link:}  Origin / Threshold / Love-as-duty.}{\VLabel{Question:}  What becomes sacred because it is real?}
